# Recode: Factor → Factor

```{r,echo=FALSE}
load("erdda-cabinet.Rds")
```

A function from the `plyr` package is used here.

```{r}
library(plyr)
```

## Example 1: Change one level or character

The variable that stores the country names looks like this.

```{r}
table(cabinet$cty)
```

You probably saw that the value for the Netherlands is `the Netherlands`.
If you want to change the value to `The Netherlands`, you can use the 
`revalue` function.

`revalue` takes a named character vector, in which the new value is the 
value of the element and the old value is the name of the element.


```{r}
newfact <- revalue(cabinet$cty, c("the Netherlands"="The Netherlands"))
```

The outcome looks like this.

```{r}
table(newfact)
```


## Example 2: Collapse several levels to one using revalue

I want to generate new variable that stores the region a country is in.

The first step is to copy the `country` variable in the data frame.

```{r}
cabinet$region <- cabinet$cty
```

Then I construct a vector to change the first batch of countries.

```{r}
eu.west <- c("Austria", "Belgium", "France", "Germany", 
             "Ireland", "Italy", "Luxembourg", "the Netherlands", 
             "Portugal", "Spain", "United Kingdom")
changing <- rep("western europe", length(eu.west))
names(changing) <- eu.west
changing
```

The result 

## Example 3: Collapse several levels to one using a function

[Example 2](#example2) above will probably look a little complicated. An
easier way to achieve the same functionality may be to use a function.

```{r}
regionalize <- function(cty) {
  eur.west <- c("Austria", "Belgium", "France", "Germany", 
               "Ireland", "Italy", "Luxembourg", "the Netherlands", 
               "Portugal", "Spain", "United Kingdom")
  eur.north <- c("Denmark", "Finland", "Iceland", "Norway", "Sweden",
                "Estonia", "Latvia", "Lithuania")
  eur.central <- c("Bulgaria", "Czech Republic", "Hungary", "Poland", 
                   "Romania", "Slovakia", "Slovenia")
  eur.south <- c("Greece", "Cyprus", "Malta")
  
  if (cty %in% eur.west) return("western europe")
  if (cty %in% eur.north) return("northern europe")
  if (cty %in% eur.central) return("central europe")
  if (cty %in% eur.south) return("southern europe")
  
  return(NA)
}
```

